---
title: "Lab 2.3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 2.3.1 Basic Commands

* create a vector of numbers

```{r}
x <- c(1,3,2,5)
x

x = c(1,6,2)
x
y = c(1,4,3)
```


* check their length

```{r}
length(x)
length(y)
```


* list of all of the objects

```{r}
ls()
rm(x,y) # to remove all objects at once: rm(list=ls())
ls()
```


* matrix

```{r}
x = matrix(data=c(1,2,3,4), nrow=2, ncol=2) # x=matrix(c(1,2,3,4), 2,2)
x

matrix(c(1,2,3,4), 2,2, byrow=TRUE)

sqrt(x)
x^2
```


* random normal variables

```{r}
x = rnorm(50)
y = x+rnorm(50, mean=50, sd=.1)
cor(x,y)

set.seed(1303)
rnorm(50)
```


* compute the mean and variance

```{r}
set.seed(3)
y = rnorm(100)

mean(y)
var(y)
sqrt(var(y))
sd(y)
```


## 2.3.2 Graphics

* plot

```{r}
x = rnorm(100)
y = rnorm(100)
plot(x, y)
plot(x, y, xlab="this is the x-axis", ylab="this is the y-axis", main="Plot of X vs Y")
```

* save the output

```{r}
pdf("Figure.pdf")
plot(x, y, col="green")
dev.off() # indicates to R that we are done creating the plot
```

* sequence

```{r}
x = seq(1, 10)


x = 1:10
x

x = seq(-pi, pi, length=50)
x
```

* contour plot

```{r}
y = x
f = outer(x, y, function(x,y) cos(y)/(1+x^2))
contour(x, y, f)
contour(x, y, f, nlevels=45, add=T)

fa = (f-t(f))/2
contour(x, y, fa, nlevels=15)

image(x, y, fa)
persp(x, y, fa)
persp(x, y, fa, theta=30)
persp(x, y, fa, theta=30, phi=20)
persp(x, y, fa, theta=30, phi=70)
persp(x, y, fa, theta=30, phi=40)


```


## 2.3.3 Indexing Data

* select elements

```{r}
A = matrix(1:16, 4, 4)
A
A[2,3]

# rows 1, 3 / cols 2, 4
A[c(1,3), c(2,4)]

# rows 1:3 / cols 2:4
A[1:3, 2:4]

# rows 1:2 / all cols
A[1:2,]

# all rows / cols 1:2
A[,1:2]

# row 1 / all cols
A[1,]

# rows except 1, 3 / all cols
A[-c(1,3),]

# rows excpet 1, 3 / cols except 1, 3, 4
A[-c(1,3), -c(1,3,4)]

# number of rows, number of cols
dim(A)
```


## 2.3.4 Loading Data

* read data

```{r}
Auto = read.table("../../../../datasets/Auto.data", header=T, na.strings="?")
fix(Auto)
dim(Auto)
Auto[1:4,]
```

* omit the missing data
```{r}
Auto = na.omit(Auto)
dim(Auto)
names(Auto)
```


## 2.3.5 Additional Graphical and Numerical Summaries

* plot the data

```{r}
plot(Auto$cylinders, Auto$mpg)

# alternative way
attach(Auto)
plot(cylinders, mpg)
```

* qualitative variables

```{r}
cylinders = as.factor(cylinders)

plot(cylinders, mpg)
plot(cylinders, mpg, col="red")
plot(cylinders, mpg, col="red", varwidth=T)
plot(cylinders, mpg, col="red", varwidth=T, horizontal=T)
plot(cylinders, mpg, col="red", varwidth=T, xlab="cylinders", ylab="MPG")
```

* histogram

```{r}
hist(mpg)
hist(mpg, col=2) # same effect as col="red"
hist(mpg, col=2, breaks=15)
```

* scatterplot

```{r}
pairs(Auto)

# produce scatterplots for just a subset of the variables
pairs(~ mpg + displacement + horsepower + weight + acceleration, Auto)
```

* summary

```{r}
# numerical sujmary of each variable in the Auto dataset
summary(Auto)

# produce a summary of just a single variable
summary(mpg)
```
