---
title: "Lab 3.6"
outhor: "Seonho Kim<ksseono@gmail.com>"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 3.6.1 Libraries

* load libraries

```{r}
# install.packages("ISLR")
# install.packages("MASS")
library(ISLR)
library(MASS)
```

## 3.6.2 Simple Linear Regression

* `Boston` dataset

```{r}
fix(Boston)
names(Boston)
```

* fit a simple linear regreesion model

```{r}
# response: medv / predictor: lstat / dataset: Boston
lm.fit = lm(medv~lstat, data=Boston)

# model information
lm.fit
```

```{r}
summary(lm.fit)
```

```{r}
names(lm.fit)
```

```{r}
coef(lm.fit)
```

* obtain a confidence interval for the coefficient

```{r}
confint(lm.fit) 
```

* produce 95% confidence/prediction intervals for the prediction (medv~lstat)

```{r}
predict(lm.fit, data.frame(lstat=c(5, 10, 15)), interval="confidence")
predict(lm.fit, data.frame(lstat=c(5, 10, 15)), interval="prediction")
```

* plot the least squares regressin line

```{r}
attach(Boston)
plot(lstat, medv)
abline(lm.fit)
```

```{r}
plot(lstat, medv)
abline(lm.fit, lwd=3)
```

```{r}
plot(lstat, medv)
abline(lm.fit, lwd=3, col="red")
```

```{r}
plot(lstat, medv, col="red")
```

```{r}
plot(lstat, medv, pch=20)
```

```{r}
plot(lstat, medv, pch="+")
```

```{r}
plot(1:20, 1:20, pch=1:20)
```

* diagnostic plots

```{r}
par(mfrow=c(2,2)) # split the screen
plot(lm.fit)
```

* residuals

```{r}
par(mfrow=c(1,2))
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
```

* leverage statistics

```{r}
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```


## 3.6.3 Multiple Linear Regression

* fit a multiple linear regression model 

```{r}
lm.fit = lm(medv~lstat+age, data=Boston)
summary(lm.fit)
```

* perform a regression using all of the predictors with short-hand

```{r}
lm.fit= lm(medv~., data=Boston)
summary(lm.fit)
```

* compute VIF(variance inflation factors) using car package

```{r}
# install.packages("car")
library(car)
vif(lm.fit)
```

* regression using all predictors except `age`

```{r}
lm.fit1 = lm(medv~.-age, data=Boston)
summary(lm.fit1)

# alternative way: using update() function
lm.fit1 = update(lm.fit, ~.-age)
```


## 3.6.4 Interaction Terms

* include an interaction term

```{r}
# lstat*age: lstat, age, lstat x age
summary(lm(medv~lstat*age, data=Boston))
```


## 3.6.5 Non-linear Transformations of the Predictors

* perform a regression of medv onto `lstat` and `lstat^2` with function `I()`

```{r}
lm.fit2 = lm(medv~lstat+I(lstat^2))
summary(lm.fit2)
```

* use the `anova()` function to quantify which is superior to the linear fit

```{r}
lm.fit = lm(medv~lstat)
anova(lm.fit, lm.fit2)

# => lm.fit2(containing lstat^2) is far superior
```

```{r}
par(mfrow=c(2,2))
plot(lm.fit2)
```

* create the polynomial within `lm()`

```{r}
# produces a fifth-order ploynomial fit
lm.fit5 = lm(medv~poly(lstat, 5))
summary(lm.fit5)
```

* log transformation

```{r}
summary(lm(medv~log(rm), data=Boston))
```


## 3.6.6 Qualitative Predictors

* `Carseats` data

```{r}
library(ISLR)
fix(Carseats)
names(Carseats)
```


* fit a multiple regression model
  * includes some interaction term
  * generates dummy variables automatically for `ShelveLoc` by R: `ShelveLocGood`, `ShelveLocMedium`
  
```{r}
lm.fit = lm(Sales~.+Income:Advertising+Price:Age, data=Carseats)
summary(lm.fit)
```

* dummay variables

```{r}
attach(Carseats)
contrasts(ShelveLoc)
```


## 3.6.7 Writing Functions

* create a function: `LoadLibraries()`
```{r}
LoadLibraries = function() {
  library(ISLR)
  library(MASS)
  print("The libraries have been loaded.")
}
```

```{r}
LoadLibraries
```

```{r}
LoadLibraries()
```


