---
title: "Lab 3.6"
outhor: "Seonho Kim<ksseono@gmail.com>"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 3.6.1 Libraries

* load libraries

```{r}
# install.packages("ISLR")
# install.packages("MASS")
library(ISLR)
library(MASS)
```

## 3.6.2 Simple Linear Regression

* Boston dataset

```{r}
fix(Boston)
names(Boston)
```

* fit a simple linear regreesion model

```{r}
# response: medv / predictor: lstat / dataset: Boston
lm.fit = lm(medv~lstat, data=Boston)

# model information
lm.fit
```

```{r}
summary(lm.fit)
```

```{r}
names(lm.fit)
```

```{r}
coef(lm.fit)
```

* obtain a confidence interval for the coefficient

```{r}
confint(lm.fit) 
```

* produce 95% confidence/prediction intervals for the prediction (medv~lstat)

```{r}
predict(lm.fit, data.frame(lstat=c(5, 10, 15)), interval="confidence")
predict(lm.fit, data.frame(lstat=c(5, 10, 15)), interval="prediction")
```

* plot the least squares regressin line

```{r}
attach(Boston)
plot(lstat, medv)
abline(lm.fit)
```

```{r}
plot(lstat, medv)
abline(lm.fit, lwd=3)
```

```{r}
plot(lstat, medv)
abline(lm.fit, lwd=3, col="red")
```

```{r}
plot(lstat, medv, col="red")
```

```{r}
plot(lstat, medv, pch=20)
```

```{r}
plot(lstat, medv, pch="+")
```

```{r}
plot(1:20, 1:20, pch=1:20)
```

* diagnostic plots

```{r}
par(mfrow=c(2,2)) # split the screen
plot(lm.fit)
```

* residuals

```{r}
par(mfrow=c(1,2))
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
```

* leverage statistics

```{r}
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```


## 3.6.3 Multiple Linear Regression

* fit a multiple linear regression model 

```{r}
lm.fit = lm(medv~lstat+age, data=Boston)
summary(lm.fit)
```

* perform a regression using all of the predictors with short-hand

```{r}
lm.fit= lm(medv~., data=Boston)
summary(lm.fit)
```

* compute VIF(variance inflation factors) using car package

```{r}
# install.packages("car")
library(car)
vif(lm.fit)
```

* regression using all predictors except age

```{r}
lm.fit1 = lm(medv~.-age, data=Boston)
summary(lm.fit1)

# alternative way: using update() function
lm.fit1 = update(lm.fit, ~.-age)
```


## 3.6.4 Interaction Terms

* include an interaction term

```{r}
# lstat*age: lstat, age, lstat x age
summary(lm(medv~lstat*age, data=Boston))
```


